Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-14 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
introduction 初稿完成

Universal adversarial perturbations (UAPs)

All the above methods can fool object trackers successfully. However, these attack methods craft the perturbations for each video independently, which comes at a non-negligible cost.
\textcolor{black}{Can we find the universal perturbations that fool a state-of-the-art deep Siamese trackers on all natural videos? We show in this paper the existence of such universal perturbations that cause the tracker to track object along any specified trajectory.}
Specifically, we aim to attack the tracker by adding an imperceptible perturbation to the template image and pasting a \textit{fake target}, i.e., a small adversarial patch into the search image adhering to the predefined trajectory, so that tracker outputs the location/size of the fake target instead of the real target.
\textcolor{black}{Different from the existing attack methods which are intrinsic dependent on videos, we generate the perturbations that can fool the network on most natural videos. Perturbing a new target then only involves the mere addition/paste operation of the universal perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.}
Overall, our contributions can be summarized as follows:
\begin{itemize}
\item We show the existence of universal video-agnostic perturbations for state-of-the-art deep Siamese trackers. To the best of our knowledge, this is the first work to perform universal targeted attack against the visual object tracking task.
\item We propose an end-to-end pipeline to generate the universal perturbations using large scale object tracking dataset.
\item Unlike most existing attack methods which only attack the classification branch of the tracker, we simultaneously manipulate the classification and bounding box regression result of the Siamese tracker.
\item Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} datasets demonstrate that our method can effectively fool the Siamese trackers in a targeted attack manner, which comes at virtually no cost.
\end{itemize}

>>>>

Universal adversarial perturbation (UAP) \cite{UAP} is an image-agnostic perturbation which can fool most images from a data distribution. Being universal, UAPs can be conveniently exploited to perturb unseen datapoints on-the-fly without extra computation. Therefore, UAPs are particularly useful when attacking real-time applications deployed on platforms with limited computing resources.
However, no existing work has touched the topic of attacking the Siamese trackers using UAPs, because it is difficult to apply existing UAPs in Siamese trackers directly. The reasons come from two aspects.
\begin{itemize}
\item Different input. Most UAPs are designed for typical neural networks, which usually accept one image as input; while Siamese-based tracking networks accept two inputs: the template image and the search image.
\item Different goals. The goal of existing UAP methods is to disturb unary and binary model outputs for single instance; while we need to use universal perturbations to mislead Siamese trackers along with a specified trajectory.
\end{itemize}

In this paper, we make the first attempt in finding the universal perturbations that fool a state-of-the-art deep Siamese trackers on all natural videos. We show in this paper the existence of such universal perturbations that cause the tracker to track object along any specified trajectory.
Specifically, we aim to attack the tracker by adding an imperceptible perturbation to the template image and pasting a \textit{fake target}, i.e., a small adversarial patch into the search image adhering to the predefined trajectory, so that tracker outputs the location/size of the fake target instead of the real target.

\textcolor{black}{Different from the existing attack methods which are intrinsic dependent on videos, we generate the perturbations that can fool the network on most natural videos. Perturbing a new target then only involves the mere addition/paste operation of the universal perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.}
Overall, our contributions can be summarized as follows:
\begin{itemize}
\item We show the existence of universal video-agnostic perturbations for state-of-the-art deep Siamese trackers. To the best of our knowledge, this is the first work to perform universal targeted attack against the visual object tracking task.
\item We propose an end-to-end pipeline to generate the universal perturbations using large scale object tracking dataset.
\item Unlike most existing attack methods which only attack the classification branch of the tracker, we simultaneously manipulate the classification and bounding box regression result of the Siamese tracker.
\item Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} datasets demonstrate that our method can effectively fool the Siamese trackers in a targeted attack manner, which comes at virtually no cost.
\end{itemize}
